article title

### 2022-07-13 article.tex
Refactor \cite

Here is a single citation. \cite{wheeler2006}

@@

\newpage
\section{References}
\nocite{*}
\printbibliography[heading=none]
\label{sec:references}

>>>>

Here is a single citation without prenote and postnote. The definitive book on MSA is by Wheeler \cite{wheeler2006}.

Here is a single citation with prenote only. The definitive book on SPC is by \cite[Wheeler][]{wheeler2006}.

Here is a single citation with prenote and postnote. For further details on $C_\text{pm}$, \cite[see][pages 1-10]{chan1988}.

@@

\newpage
\section{References}
% \nocite{*}
\printbibliography[heading=none]
\label{sec:references}
